### 2015-08-16 LaTeX/RhodiumIntro.tex
Mexico -> Nigeria & Cameroon
Really? Ugh.

Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth. Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time. Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and projected that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}. In that same year, \emph{Barron's} ran a headline titled, ``Is Mexico the New China?'' \citep{kapadia:2012}. This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plummeted. \citet{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.'' ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''

>>>>

Further, few in the literature have sought to explain puzzling cases of domestic armed conflicts that have little impact on macroeconomic growth. Nigeria and Cameroon, for instance, have both been engaged in violent conflict with Boko Haram, a group of militants determined to establish an Islamic state in West Africa. In Nigeria, the death toll has steadily risen since 2011; the Council on Foreign Relations estimates that the conflict had resulted in over 40,000 casualties by mid-2015 \citep{cfr:2015}. However, Boko Haram primarily operates in the rural and relatively less populated north-eastern regions of Nigeria and Cameroon. During this conflict, both countries have maintained robust economic growth. When Nigeria rebased its economy in 2014, it overtook South Africa as the continent's largest economy.

%Further few in the literature have sought to explain puzzling cases of domestic armed conflict having little impact on macroeconomic growth. Mexico, for example, has been engaged in a drug war since December 2006 and the number of deaths stemming from this civil conflict have only increased since that time. Yet, even as fatalities due to the drug war reached new peaks, in 2012, Vikram Pandit of Citigroup cited Mexico as being extremely well poised for growth and projected that its economy may surpass that of its much larger regional rival, Brazil, within a decade \citep{vardi:2012}. In that same year, \emph{Barron's} ran a headline titled, ``Is Mexico the New China?'' \citep{kapadia:2012}. This contrasts greatly with the economic fortunes of other countries in the midst of civil war where economies have plummeted. \citet{collier:elliott:etal:2003}, for instance, describe civil war as ``development in reverse.'' ``The overall economic and political legacy from civil war,'' they write, ``is thus sufficiently adverse that rapid recovery is unlikely.''

### 2015-08-16 LaTeX/RhodiumTheory.tex
Mexico -> Nigeria & Cameroon
Really? Ugh.

While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral. India, for instance, has faced challenges by armed groups in its north-east for half a century. However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India. Indeed, for much of this period, India has experienced relatively robust economic growth. In figure \ref{fig:indiaMap}, we show the geographic distribution of conflict in India from 1989 to 2007 again using the PRIO conflict site database. The story from this map is clearly quite stark from that of Colombia. Whereas in Colombia conflict had come right to the gates of major cities, in India conflict clearly has been centered in the peripheries.

@@

It is important to note that Mexico does not appear in the civil war dataset chosen for this study. The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country \citep[p.1]{themner:2014}. Nonetheless, we want to reiterate that this instance of armed conflict, of the magnitude typically associated with civil war, conforms to the expectations of our theory. Mexico, now nearly a decade into a violent and complicated conflict between several organized criminal enterprises and the federal government, has maintained healthy economic performance. For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities. \citet{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.'' Meanwhile, several majors cities including the capital, Mexico City, have experienced relatively low levels of cartel violence.

>>>>

While FARC seems to exploit its ability to target areas of economic importance including cities, other insurgencies tend to be more peripheral. India, for instance, has faced challenges by armed groups in its north-east for half a century. However, this area of India is remote, primarily agrarian, and relatively less populous than other parts of India. Indeed, for much of this period, India has experienced relatively robust economic growth. In figure \ref{fig:indiaMap}, we show the geographic distribution of conflict in India from 1989 to 2007 again using the PRIO conflict site database. The story from this map is clearly quite stark from that of Colombia. Whereas in Colombia conflict had come right to the gates of major cities, in India conflict clearly has been confined to the periphery.

@@

%It is important to note that Mexico does not appear in the civil war dataset chosen for this study. The UCDP definition of civil war requires that the conflict be fought over an ``incompatibility that concerns government and/or territory,'' a criteria not strictly met by the organized crime violence experienced by the country \citep[p.1]{themner:2014}. Nonetheless, we want to reiterate that this instance of armed conflict, of the magnitude typically associated with civil war, conforms to the expectations of our theory. Mexico, now nearly a decade into a violent and complicated conflict between several organized criminal enterprises and the federal government, has maintained healthy economic performance. For much of this time, the cartel violence generally occurred in rural areas along drug trafficking routes and not within major cities. \citet{beittel:2011} writes in 2011 that ``drug trafficking-related killings remain concentrated in a relatively few cities.'' Meanwhile, several majors cities including the capital, Mexico City, have experienced relatively low levels of cartel violence.
